SpatialEpi

### 2021-07-26 README.Rmd
Fixed all url's

[![R-CMD-check](https://github.com/rudeboybert/SpatialEpi/workflows/R-CMD-check/badge.svg)](https://github.com/rudeboybert/SpatialEpi/actions)
[![CRAN_Status_Badge](http://www.r-pkg.org/badges/version/SpatialEpi)](http://cran.r-project.org/package=SpatialEpi) [![CRAN RStudio mirror downloads](http://cranlogs.r-pkg.org/badges/SpatialEpi)](http://www.r-pkg.org/pkg/SpatialEpi)

>>>>

[![R-CMD-check](https://github.com/rudeboybert/SpatialEpi/workflows/R-CMD-check/badge.svg)](https://github.com/rudeboybert/SpatialEpi/actions)
[![CRAN_Status_Badge](https://www.r-pkg.org/badges/version/SpatialEpi)](https://cran.r-project.org/package=SpatialEpi) [![CRAN RStudio mirror downloads](https://cranlogs.r-pkg.org/badges/SpatialEpi)](https://www.r-pkg.org/pkg/SpatialEpi)
